Tail Indices and Scale Parameters in Financial Time Series

### 2017-03-01 papers/FX/draft.tex
Accomodating the mistake pointed out by Thomas.

\subsubsection[in case gamma > 1]{in case $\gamma > 1$}
In this section we consider power utility functions of
\eqref{eq:power_utility} with $\gamma > 1$. For convenience,
let $\xi = \gamma - 1$. In this case, we assume the following
distribution function $F(\cdot)$ of the equity return:
\begin{equation}
  \label{eq:X_distr}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x \leq 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and $K > 0$.
Equation
\eqref{eq:xxie0} can be re-arranged as
\begin{eqnarray}
u(v) &=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) \P[C < \delta v] \nonumber \\
&=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(-q) \label{eq:functional}
\end{eqnarray}
where
\begin{eqnarray*}
  q(r, \phi) &:=& -\ln \left( {
    \delta v - (1 - \phi) e^r
    \over
    \phi
} \right)
\end{eqnarray*}
Note $C < \delta v$ implies
\[
X < -q(r, \phi)
\]
The right-hand-side of \eqref{eq:functional} is a functional of the
distribution function of $X$ via \eqref{eq:xxie1}. For convenience
we denote it $\mathcal U(\cdot)$, i.e.
\[
\mathcal U F (\alpha, \beta, K, K', \phi)
= 
\E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(-q)
\]
In the rest of this section we write $q$ for $q(r, \phi)$
for convenience. We have
\begin{eqnarray}
  && \mathcal U F (\alpha, \beta, K, K', \phi) \nonumber \\
  &=& \underbrace{
  -{\alpha K^\alpha \over \xi} p
  \int_{-\infty}^0
      {
       1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
      }
  {1 + b \1{x < -q} \over (K - x)^{\alpha + 1}} dx
  }_{J_1} \nonumber \\
  && -{\beta K'^\beta \over \xi} (1 - p)
  \int_{0}^\infty
  {
   1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
  }
  {1 + b \1{x < -q} \over (K' + x)^{\beta + 1}} dx \nonumber \\
  &&
  \underbrace{
    -b u(\delta v) p {K^\alpha \over (K + q)^\alpha} \1{q \geq 0}
  }_{J_2}
  - b u(\delta v) \left[
    1 - (1 - p) {
      K'^\beta
      \over
      (K' - q)^\beta
    } \1{q < 0}
  \right]
  \label{eq:xxie1.0}
\end{eqnarray}

@@

    &=& \pd{J_1}{\alpha} + \pd{J_2}{\alpha} > 0

@@

  The 2nd term is easily computed:

@@

    \pd{J_2}{\alpha} &=& b u(\delta v) p \1{q \geq 0}
      {K \over K + q}
    \right)^\alpha
      1 + {q \over K}
    \right) > 0
  As for the 1st term we have
  \begin{enumerate}[i.]
  \item When $q \geq 0$,
      && \pd{J_1}{\alpha}(\alpha, \beta, K, K', \hat \phi) \\

@@

        {\alpha p K^\alpha \over \xi}
          (1 + b)\int_{-\infty}^{-q} +
          \int_{-q}^0
        \right] \right. \\
      && \left.
        \left\{

@@

        \right\}

@@

          (1 + b)\int_{q}^{\infty} +
          \int_{0}^q

@@

      L_1 &<& {

@@

      } \int_0^\infty

@@

@@

@@

    {p \over c \xi}

@@

    \times
    \left\{
      \begin{array}{ll}
        1 & \text{ if } 0 < x < q \\
        (1 + b) & \text{ if } x > q \\
      \end{array}
    \right.

@@

      \E Y &:=& {p \over c \xi}
        (1 + b)\int_{q}^{\infty} +
        \int_{0}^q

@@

        (1 + b)\int_{q}^{\infty} +
        \int_{0}^q

@@

        p [(K + q)^{-\alpha} b + K^{-\alpha}] K^\alpha

@@

        \alpha \xi [(1 - \hat\phi) e^r + \hat\phi]^\xi

@@

    Meanwhile
      c &<& {p \over \xi}
        (1 + b)\int_{q}^{\infty} +
        \int_{0}^q
        \alpha K^\alpha p \left[

@@

        \xi (\alpha + 1) (1 - \hat\phi)^\xi e^{r \xi}

@@

  \item When $q < 0$, it follows from \eqref{eq:xxie1.0}:
    \begin{eqnarray*}
      && \opd{\alpha}J_1(\alpha, \beta, K, K', \hat\phi) \\
      &=& \opd{\alpha} \left[
        -{\alpha K^\alpha \over \xi} p
        \int_{-\infty}^0
            {
              1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
            }
            {1 + b \over (K + x)^{\alpha + 1}} dx
        \right]
    \end{eqnarray*}
  \end{enumerate}
  So the same calculation as in the previous case carries through
  with 0 substituted for $q$. The same conclusion of
  \[
  \pd{\mathcal U(F)}{\alpha}(\alpha, \beta, K, K', \hat \phi) > 0
  \]
  stands.
\end{proof}
Since $u(v) + b u(\delta v)$ given in \eqref{eq:xxie1.0} as a
functional of the distribution function of $X$ is increasing with the
lower tail index $\alpha$, all agents guided by this class of utility
functions will seek the largest $\alpha$ found in a stock group e.g.
a sector. As a result, one can expect all the actively traded equities
in the group to feature the same $\alpha$. In section
\ref{sec:data_analysis} we analyse real-world data of stock returns to
verify this conclusion.

>>>>

\subsubsection[in case gamma > 1]{in case $\gamma > 1$}
In this section we consider power utility functions of
\eqref{eq:power_utility} with $\gamma > 1$. For convenience,
let $\xi = \gamma - 1$. In this case, we assume the following
distribution function $F(\cdot)$ of the equity return:
\begin{equation}
  \label{eq:X_distr}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x \leq 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and $K > 0$.
Equation
\eqref{eq:xxie0} can be re-arranged as
\begin{eqnarray}
u(v) &=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) \P[C < \delta v] \nonumber \\
&=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q) \label{eq:functional}
\end{eqnarray}
where
\begin{eqnarray*}
  q(r, \phi) &:=& \ln \left( {
    \delta v - (1 - \phi) e^r
    \over
    \phi
} \right) = \ln\left(
e^r + {\delta v - e^r \over \phi}
\right)
\end{eqnarray*}
Note $C < \delta v$ implies
\[
X < q(r, \phi)
\]
Naturally, if an agent invests in a risky asset instead of a riskless
bond, he expects to obtain a higher return from the risky asset than
he is guarranteed from the riskless bond. In our notation,
this means $\delta v > e^r$, which implies $q(r, \phi) > 0$.
The right-hand-side of \eqref{eq:functional} is a functional of the
distribution function of $X$ via \eqref{eq:xxie1}. For convenience
we denote it $\mathcal U(\cdot)$, i.e.
\[
\mathcal U F (\alpha, \beta, K, K', \phi)
= 
\E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q(r, \phi))
\]
Hereafter we abbreviate $q(r, \phi)$ to just $q$. We have
\begin{eqnarray}
  && \mathcal U F (\alpha, \beta, K, K', \phi) \nonumber \\
  &=& \underbrace{
  -{\alpha K^\alpha \over \xi} p
  \int_{-\infty}^0
      {
       1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
      }
  {1 + b \over (K - x)^{\alpha + 1}} dx
  }_{J_1} \nonumber \\
  && -{\beta K'^\beta \over \xi} (1 - p)
  \int_{0}^\infty
  {
   1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
  }
  {1 + b \1{x < q} \over (K' + x)^{\beta + 1}} dx \nonumber \\
  &&
  - b u(\delta v) \left[
    1 - (1 - p) {
      K'^\beta
      \over
      (K' - q)^\beta
    }
  \right]
  \label{eq:xxie1.0}
\end{eqnarray}

@@

    &>& 0

@@

@@

      && \pd{\mathcal U(F)}{\alpha}(\alpha, \beta, K, K', \hat \phi) \\

@@

        {\alpha p K^\alpha \over \xi} (1 + b)
        \int_{-\infty}^{0}

@@

@@

          (1 + b)\int_{0}^{\infty}

@@

      L_1 &<&

@@

      \int_0^\infty

@@

      \int_{0}^{\infty}
        dx \over (K + x)^{\alpha + 2}
        \alpha p (1 + b)
        K \xi (\alpha + 1) (1 - \phi)^\xi e^{r \xi}

@@

      \label{eq:c_lower_bound}

@@

    {p (1 + b)\over c \xi}

@@

@@

      \E Y &:=& {p (1 + b)\over c \xi}
      \int_0^\infty

@@

      {p (1 + b) \over \xi}
      \int_{0}^{\infty}

@@

        p (1 + b)

@@

        \alpha \xi ((1 - \phi) e^r + \phi)^\xi

@@

    Meanwhile, as computed earlier in \eqref{eq:c_lower_bound}
      c < {
        \alpha p (1 + b)

@@

        K \xi (\alpha + 1) (1 - \phi)^\xi e^{r \xi}

@@

\end{proof}
Since $u(v) + b u(\delta v)$ given in \eqref{eq:xxie1.0} as a
functional of the distribution function of $X$ is increasing with the
lower tail index $\alpha$, all agents guided by this class of utility
functions will seek the largest $\alpha$ found in a stock group e.g.
a sector. As a result, one can expect all the actively traded equities
in the group to feature the same $\alpha$. In section
\ref{sec:data_analysis} we analyse real-world data of stock returns to
verify this conclusion.
